Trends of SDR in Thessaloniki

### 2023-07-15 Article.Rmd
Commit 2023-07-15 23:09

where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $w\;m^{-2}$.

The following criteria and thresholds were used to identify clear-sky conditions.
Each criterion was applied for a running window of $`r nt`$ consecutive measurements/minutes, and the characterization is applied at the center value of the window.
A data point is consider as under cloud-sky condition if it fails to pass any of the criteria, the rest data points are characterized as clear-sky.

>>>>

where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $\text{w}\;\text{m}^{-2}$.

The criteria that were used to identify whether a measurement was taken
under clear-sky conditions are presented below.
A data point is flagged
as "clear-sky" if all criteria are satisfied.
Each criterion was applied
for a running window of $`r nt`$ consecutive one-minute measurements, and
the characterization is assigned to the central value of the window.
Each parameter was calculated both from the measurements and the
clear-sky model.
The allowable range of variation is defined by the
model-derived value of the parameter multiplied by a factor plus an
offset. [.... .expanded the description ....]{.comment-start id="4"
author="A N" date="2023-07-15T22:48:13Z"}The factors and offsets were
determined empirically, by manual inspecting each filters performance on
selected days, and adjusting them accordingly, during the iterative
process.[[]{.comment-end id="4"}]{.insertion author="A N"
date="2023-07-15T22:48:13Z"}
